When two-point correlation function fails to describe a structure...

### 2024-03-07 paper.tex
Fix some statements about non-palindrome factors

A reciprocal polynomial of $f(x)$ has the same degree as $f$. Suppose $f$
factors into $M$ different factors in $\mathbb{Z}[x]$:
\begin{equation*}
  f(x) = \prod_{i=1}^M f_i(x)
\end{equation*}
The image of the two-point function is then
\begin{equation*}
  s(x) = f(x)f(x^{-1}) = \prod_{i=1}^M f_i(x) \prod_{i=1}^M f_i(x^{-1})
\end{equation*}
Let now select $1 \le L < M$ non-palindrome factors
$f_{r_1}, f_{r_2}, \dots, f_{r_L}$ of $f$ and replace them with their
reciprocals. Obviously, the resulting correlation function won't change:
\begin{equation*}
  s(x) = \underbrace{\prod_{i=1}^L x^{\deg f_{r_i}} f_{r_i}(x^{-1}) \prod_{i=1}^{M-L} f_{o_i}(x)}_{\tilde{f}(x)}
  \underbrace{\prod_{i=1}^L x^{-\deg f_{r_i}} f_{r_i}(x) \prod_{i=1}^{M-L} f_{o_i}(x^{-1})}_{\tilde{f}(x^{-1})}
\end{equation*}
where $o_1, o_2, \dots, o_{M-L}$ run through indices of original (not replaced)
factors. Now recombining factors into $\tilde{f}(x)$ and $\tilde{f}(x^{-1})$ we
obtain a polynomial $\tilde{f}$ with the same degree as $f$ and $f(0) = \tilde{f}(0)$.
Now note that with this additional demand on the free coefficient, we can
restrict the group of transforms \cref{eq:group} to a subgroup $\{S_0, R\}$
because a non-zero shift will change the degree of $f$ which is not allowed. We
have two possible outcomes regarding $\tilde{f}$:
\begin{itemize}
\item Only at most one factor in $f_{r_1}, \dots, f_{r_L}$ is not a
  palindrome. This gives us $\tilde{f}(x) = f(x^{-1})$ which is a trivial
  collision.
\item At least two factors in $f_{r_1}, \dots, f_{r_L}$ are not palindromes. In
  this case $\tilde{f} \ne f$ and cannot be obtained from $f$ using transforms
  in the subgroup $\{S_0, R\}$.
\end{itemize}

>>>>

A reciprocal polynomial of $f(x)$ has the same degree as $f$. Suppose $f$
factors into $M$ different factors in $\mathbb{Z}[x]$:
\begin{equation*}
  f(x) = \prod_{i=1}^M f_i(x)
\end{equation*}
The image of the two-point function is then
\begin{equation*}
  s(x) = f(x)f(x^{-1}) = \prod_{i=1}^M f_i(x) \prod_{i=1}^M f_i(x^{-1})
\end{equation*}
Let now select all non-palindrome factors $f_{r_1}, f_{r_2}, \dots, f_{r_L}$ of
$f$, $0 \le L \le M$ and replace them with their reciprocals. Obviously, the
resulting correlation function won't change:
\begin{equation*}
  s(x) = \underbrace{\prod_{i=1}^L x^{\deg f_{r_i}} f_{r_i}(x^{-1}) \prod_{i=1}^{M-L} f_{o_i}(x)}_{\tilde{f}(x)}
  \underbrace{\prod_{i=1}^L x^{-\deg f_{r_i}} f_{r_i}(x) \prod_{i=1}^{M-L} f_{o_i}(x^{-1})}_{\tilde{f}(x^{-1})}
\end{equation*}
where $o_1, o_2, \dots, o_{M-L}$ run through indices of original (not replaced)
factors. Now recombining factors into $\tilde{f}(x)$ and $\tilde{f}(x^{-1})$ we
obtain a polynomial $\tilde{f}$ with the same degree as $f$ and $f(0) = \tilde{f}(0)$.
Now note that with this additional demand on the free coefficient, we can
restrict the group of transforms \cref{eq:group} to a subgroup $\{S_0, R\}$
because a non-zero shift will change the degree of $f$ which is not allowed. We
have two possible outcomes regarding $\tilde{f}$:
\begin{itemize}
\item Only at most one factor of $\tilde{f}$ is not a palindrome
  ($L \le 1$). This gives us $\tilde{f}(x) = f(x^{-1})$ which is a trivial
  collision.
\item At least two factors of $\tilde{f}$ are not palindromes ($L > 1$). In
  this case $\tilde{f} \ne f$ and cannot be obtained from $f$ using transforms
  in the subgroup $\{S_0, R\}$.
\end{itemize}
